Manuscript_Github_Pchabaudi_pir

### 2022-07-27 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Further investigations into the phase differences

```{r}
#Make a topGOdata object 
GOdata <- new("topGOdata", 
              ontology = "CC", 
              geneSel = function(x){x == 1},
              allGenes = z_max_diff.list$`0`,
              nodeSize = 5,
              annot = annFUN.gene2GO, 
              gene2GO = go_annotation)
resultFis <- runTest(GOdata, 
                     algorithm = "classic", 
                     statistic = "fisher")
hist(score(resultFis), 50, xlab = "p-values")
GenTable(GOdata, 
         classic = resultFis, 
         orderBy = "classic", 
         ranksOf = "classic",
         topNodes = 25) %>% 
  filter(classic < 0.05)

lapply(seq(0,4), 
       function(phase){
         GOdata <- new("topGOdata", 
                       ontology = "BP", 
                       geneSel = function(x){x == 1},
                       allGenes = getElement(z_max_diff.list, paste(phase)),
                       nodeSize = 5,
                       annot = annFUN.gene2GO, 
                       gene2GO = go_annotation)
         resultFis <- runTest(GOdata, 
                              algorithm = "classic", 
                              statistic = "fisher")
         hist(score(resultFis), 50, xlab = "p-values")
         GenTable(GOdata, 
                  classic = resultFis, 
                  orderBy = "classic", 
                  ranksOf = "classic",
                  topNodes = 25) %>% 
           filter(classic < 0.05)
       })

# showSigOfNodes(GOdata, 
#                score(resultFis), 
#                firstSigNodes = 5, 
#                useInfo = 'all')
```

@@

>>>>

```{r}
#Load for the showSigOfNodes network function.
library('Rgraphviz')

#Make a topGOdata object 
GOdata <- new("topGOdata", 
              ontology = "BP", 
              geneSel = function(x){x == 1},
              allGenes = z_max_diff.list$`1`,
              nodeSize = 5,
              annot = annFUN.gene2GO, 
              gene2GO = go_annotation)
resultFis <- runTest(GOdata, 
                     algorithm = "classic", 
                     statistic = "fisher")
plot.new()
hist(score(resultFis), 50, xlab = "p-values")
dev.off()
showSigOfNodes(GOdata,
               score(resultFis),
               firstSigNodes = 5,
               useInfo = 'all')
goRes <- GenTable(GOdata, 
         classic = resultFis, 
         orderBy = "classic", 
         ranksOf = "classic",
         topNodes = 25) %>% 
  filter(classic < 0.05)

#Get first (most significant) enriched GO id 
goID <- goRes[4, "GO.ID"]
#Show distribution of GO term genes compared to null distribution (all other genes)
print(showGroupDensity(GOdata, goID, ranks = TRUE))

#Unlist the lapply below which goes through each element of the list and 
# returns TRUE is the go_id is listed for that gene.
#This makes a TRUE/FALSE index for the list/names of the list which can get 
# the genes associated with that GO id.
goID_genes <- names(go_annotation)[unlist(
  lapply(go_annotation, 
         function(go_ids){
           any(goID %in% go_ids)
         })
)]

draw_heatmap_zscore(zscore_list = chab_z.list,
                    filter_genes_vector = names(z_max_diff.list$`1`[z_max_diff.list$`2` == 1]),
                    gene_ordering_vector = phaseogram_time_order$rMT$zscore_order$Geneid,
                    threshold_tpm = 1,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = TRUE)
```

```{r}

lapply(seq(0,4), 
       function(phase){
         GOdata <- new("topGOdata", 
                       ontology = "BP", 
                       geneSel = function(x){x == 1},
                       allGenes = getElement(z_max_diff.list, paste(phase)),
                       nodeSize = 5,
                       annot = annFUN.gene2GO, 
                       gene2GO = go_annotation)
         resultFis <- runTest(GOdata, 
                              algorithm = "classic", 
                              statistic = "fisher")
         draw_heatmap_zscore(zscore_list = chab_z.list,
                             filter_genes_vector = names(
                               getElement(z_max_diff.list, paste(phase))[
                                 getElement(z_max_diff.list, paste(phase)) == 1
                               ]
                             ),
                             gene_ordering_vector = phaseogram_time_order$rMT$zscore_order$Geneid,
                             threshold_tpm = 1,
                             use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = TRUE)
         GenTable(GOdata, 
                  classic = resultFis, 
                  orderBy = "classic", 
                  ranksOf = "classic",
                  topNodes = 25) %>% 
           filter(classic < 0.05)
       })

@@

Fore node visualisation:
"Rectangles indicate the 5 most signicant terms. Rectangle color represents the relative signicance,
ranging from dark red (most signicant) to bright yellow (least signicant). For each node, some basic information
is displayed"
